WrapITK: Enhanced languages support\\ for the Insight Toolkit

### 2007-11-21 article/Article.tex
very old changes not recorded in the article
darcs-hash:20071121141637-2fc9d-78ca0005c646fdea3841c3c7ec6aaa949141c21b.gz

% Increment the release number whenever significant changes are made.
% The author and/or editor can define 'significant' however they like.
\release{0.2}

@@

  \item ITK was broken on MacOS X \cite{MacOsXWebSite} with python.

@@

@@

WrapITK defines some lists which group the types and dimensions. Those lists can be used
by the developer to create a wrappers but must {\em never} be modified.

@@

@@

  \item \verb$WRAP_IMAGE_FILTER_type(size)$ . \verb$type$ can be one of:
  \begin{itemize}
    \item \verb$USIGN_INT$ to select all the image types with unsigned integral
pixel types selected by the user
    \item \verb$SIGN_INT$ to select all the image types with signed integral
pixel types selected by the user
    \item \verb$INT$ to select all the image types with signed and unsigned integral
pixel types selected by the user
    \item \verb$REAL$ to select all the image types with real pixel types selected by the user
    \item \verb$VECTOR_REAL$ to select all the image types with \verb$Vector$
pixel types selected by the user
    \item \verb$COV_VECTOR_REAL$ to select all the image types with \verb$CovariantVector$
pixel types selected by the user
    \item \verb$RGB$ to select all the image types with \verb$RGBPixel$
pixel types selected by the user
    \item \verb$SCALAR$ to select all the image types with scalar pixel types selected by the user
    \item \verb$VECTOR$ to select all the image types with \verb$Vector$ and \verb$CovariantVector$
pixel types selected by the user
    \item \verb$ALL$ to select all the image types selected by the user.
  \end{itemize}

>>>>

% Increment the release number whenever significant changes are made.
% The author and/or editor can define 'significant' however they like.
\release{0.2.2}

@@

  \item ITK was broken on MacOS X \cite{MacOsXWebSite} with Python and Java.

@@

     \subsubsection{A simple example: MedianImageFilter}

@@

     \subsubsection{WrapITK predifined lists}

The main task of the developer is to define which template parameters are valid for a given
templated class, and interesting for the user. He also have to take care about
instantiating some templated classes according to the options selected by the user.

With WrapITK, the developer don't have to declare that a class is instantiated with the template parameters
\verb$unsigned char$, \verb$unsigned short$, and \verb$unsigned long$, but rather declares that the
templated classe can be instantiated with all the unsigned integer types choosed by the user.
To do that, WrapITK provides some already defined list which are grouping the types chosen by
the user. Those lists can be used by the developer to create a wrappers but must
{\em never} be modified.

@@

     \subsubsection{WrapITK predifined variables and naming consistency}

WrapITK defines some pairs of variables for each basic type the developer may have
to manipulate: the c++ type, and its template parameter name. The name of the type
is stored in \verb$ITKM_???$, and the c++ type in \verb$ITKT_???$.

For example, for \verb$unsigned char$, \verb$ITKM_UC$ and \verb$ITKT_UC$
are defined, with \verb|${ITKM_UC} = "UC"| and \verb|${ITKM_UC} = "unsigned char"|.

     \subsubsection{WrapITK macros}

@@

  \item \verb$WRAP_IMAGE_FILTER_type(size)$ . \verb$type$ can be one of:
  \begin{itemize}
    \item \verb$USIGN_INT$ to select all the image types with unsigned integral
pixel types selected by the user
    \item \verb$SIGN_INT$ to select all the image types with signed integral
pixel types selected by the user
    \item \verb$INT$ to select all the image types with signed and unsigned integral
pixel types selected by the user
    \item \verb$REAL$ to select all the image types with real pixel types selected by the user
    \item \verb$VECTOR_REAL$ to select all the image types with \verb$Vector$
pixel types selected by the user
    \item \verb$COV_VECTOR_REAL$ to select all the image types with \verb$CovariantVector$
pixel types selected by the user
    \item \verb$RGB$ to select all the image types with \verb$RGBPixel$
pixel types selected by the user
    \item \verb$SCALAR$ to select all the image types with scalar pixel types selected by the user
    \item \verb$VECTOR$ to select all the image types with \verb$Vector$ and \verb$CovariantVector$
pixel types selected by the user
    \item \verb$ALL_TYPES$ to select all the image types selected by the user.
  \end{itemize}
